### 2019-09-30 proglog.tex
updates program logistics

\subsubsection{Critical Conversations: Microreactors}
Microreactors are a growing area of nuclear research and the first installations have been projected for some time in the mid 2020s. They are capable of generating 1-50 MWth, which can be used directly or converted to electricity. These relatively portable reactors are capable of powering remote areas and towns with little infrastructure. UIUC has stated that it aims to be carbon neutral by 2050. The University is exploring the possibility of constructing a microreactor on campus for research and power generation, a first of its kind, in pursuit of its decarbonization goals. This panel will discuss the benefits and applications for microreactors around the world and also talk specifically about the potential market for microreactors on universities. We have a several groups on campus researching, simulating, and modelling microreactors. Faculty leading these groups would be excellent speakers on this panel.

\subsubsection{Plasma Processing in Your Pocket}
Plasma processing has become a staple in many fields of advanced manufacturing. Without plasma, modern conveniences such as smartphones and powerful computer technology would not be possible. In this panel, representatives from companies at the cutting-edge of plasma processing research will discuss how plasmas continue to revolutionize contemporary industry. Potential panelists include Brian Jurczyk, CEO of Starfire Industries, and Phi Nguyen, former Vice President and Director of Engineering at Intel Corp.

\subsubsection{Fusion: Materials for the Future}
Nuclear fusion has the potential to serve as the ultimate clean energy source, capable of supplying the world’s energy needs for millennia. Harnessing this immensely powerful energy resource requires further innovation in a variety of scientific disciplines. One of the largest remaining obstacles to fusion energy is the unprecedented strain placed on the materials from which fusion reactors are built. This panel will focus on the latest advancements in plasma facing components research and could feature panelists such as Professor David Ruzic, director of the UIUC Center for Plasma-Material Interactions, and Dr. Lauren Garrison, Weinberg Fellow at ORNL.

\subsubsection{Nuclear Policy and Legislation}
Nuclear energy is one of the most heavily regulated fields in the United States. This panel aims to enlighten attendees about how legislation is written and how non-scientist government officials might better understand the potential of nuclear energy. This panel will allow attendees to learn who is working in this area and develop a network of people devoted to issues of nuclear policy.
Rita Baranwal would be an excellent speaker on this panel because of her work for the DOE.

\subsubsection{Radiological Techonology for a Healthier and Safer Future}
From the production of medical isotopes to nuclear verification, radiological engineering will play an important role in the future of health, security, and more. This panel will illuminate some of those applications and show attendees what could be possible with radiological technology. Speakers may include Greg Piefer from SHINE and Ross Radel from Phoenix.\\

@@

\subsubsection{Science is People: Conducting Inclusive Research}
Research and technology that will help us solve the grand challenge problems of the world must also reflect the diverse needs of the people that live in it. Everyone comes to nuclear engineering from a variety of backgrounds, identities, abilities, and experiences. Saving the World One Atom at a Time means making atomic contributions. Finding ways to encourage and include even one more person in the endeavor of nuclear science is an important kind of atomic contribution. This panel works toward the goal of celebrating the people behind the science. It also serves to inspire students and

\subsubsection{Talking To Non-Scientists}
It has been shown that when members of the general public are given more scientific evidence they are less likely to shift their beliefs. While this finding is surprising to members of the scientific community, people who value data and evidence, it can be difficult to find ways to effectively communicate your research to the public. Attendees will learn how other scientists effectively communicate their results. No longer discouraged by potential resistance from the public, students will steel their resolve for working on ambitious projects that can save the world. Suzanne Hobbs Baker would be a great choice for this panel, as well as members of The Story Collider; a non-profit organization devoted to helping scientists tell stories that

\subsubsection{How to Host a Conference}
This panel is devoted to sharing the experience of this conference's planning committee with students from other schools that may want to host their own student conference. This panel is for students by students. We will discuss our process from writing a successful proposal to executing a successful conference.

@@

\subsubsection{PyNE and PyRK Workshop}
Python for Nuclear Engineering (PyNE) and Python for Reactor Kinetics (PyRK) are two open source packages with computational tools for nuclear science and engineering. The PyNE toolkit provides both a Python and a C++ API for common computational pre- and post-processing tasks in nuclear engineering. PyRK offers point kinetics implementation for nuclear reactors. This workshop will provide a hands-on tutorial for attendees to begin using PyNE and make use of its capabilities for their curriculum and research work. The Advanced Reactors and Fuel Cycles (ARFC) research group at UIUC and its collaborators will provide instructors. This workshop, alpha-tested at the University of Wisconsin will be aimed at students who can provid their own laptops and have a desire to improve their nuclear computational skills. The workshop will be approximately two hours of instruction at NCSA room 1030.

@@

Technical sessions are an integral part of every student conference. This is where students can share their research experiences, new ideas, exchange knowledge, and \textit{atomic contributions} to the big problems of the world. There are 6 technical sessions held concurrently each day. Each room will be equipped with a projectors, computers, podiums, and other necessary equipment. Each presenter is given 15 minutes to present and 5 minutes to answer questions from the audience. Presenters will be judged on significance, originality, and overall presentation (Podium Presentation Judging Form can be found in Appendix B). The divisions of the technical sessions include, but are not limited to
\begin{itemize}
	\item Accelerator Applications
	\item Aerospace Nuclear Science \& Technology
	\item Computational Medical Physics
	\item Decommissioning \& Environmental Sciences
	\item Education, Training \& Workforce Development
	\item Fuel Cycle \& Waste Management
	\item Fusion Energy
	\item Human Factors, Instrumentation \& Control
	\item Isotopes \& Radiation
	\item Materials Science \& Technology
	\item Mathematics \& Computation for Nuclear Engineering
	\item Next Generation Reactors \& Advanced Reactors
	\item Nuclear Criticality Safety
	\item Nuclear Energy Applied to Biology \& Medicine
	\item Nuclear Installations Safety
	\item Nuclear Nonproliferation
	\item Probabilistic Risk Analysis
	\item Operations \& Power
	\item Radiation Protection \& Shielding
	\item Reactor Physics
	\item Robotics \& Remote Systems
	\item Thermal Hydraulics
\end{itemize}
Practice rooms will be made available every day of the conference. We expect a total of 48 technical sessions each with 4-5 presenters. There will be an award for best graduate and best undergraduate presentation for each category.

\subsection{Poster Session}
There will be a poster session on Saturday in Illini Room C and the South Lounge. This offers nearly 1600 square feet of space and allows students an opportunity to share their research in an open environment. The poster session will be immediately adjacent to the career fair. This encourages students and professionals, that might otherwise go to one or neither, to attend both. There will be an award for best graduate and undergraduate poster.
\subsubsection{Highschool Poster Session}
We believe that attracting younger students to the field of nuclear engineering will help us grow the nuclear community. To that end we will invite high school students to present a poster on a topic of interest in the nuclear sciences. This will also add to the diversity of the conference.

\subsection{Career Fair}
The career will be held all day on Friday, from 8am to 5pm, and on Saturday from 8am to noon. It will be held in Illini Rooms A \& B, a large space that will be shared with the poster sessions on saturday to encourage students and professionals to attend both. Recruiters may mail bulkier items prior to their arrival in Champaign. All companies that sponsor the conference will be given a table at the career fair. Location will be decided in order of sponsorship amount and when the agreement was made. Universities may freely request a table at the career fair, while space is available. There will be rooms available at the Illini Union for companies to interview potential candidates.

@@

\begin{minipage}{0.5\textwidth}
\textbf{Argonne National Laboratory}\\
Located in Lemont, Illinois, Argonne works closely with universities, industry, and other national labs to help make an impact on the atomic, human, and global scale. With 14 research divisions, five national scientific user facilities, and hundreds of research partners, attendees of this tour will be exposed to the diverse areas of research in nuclear science. Argonne is two-and-a-half-hour drive away. Bus transportation will be provided. On the tour, students will be guided around the site’s scientific and engineering facilities.
\end{minipage}
\begin{minipage}{0.5\textwidth}
	\includegraphics[width=\textwidth]{argonne.png}
	\captionof{figure}{Argonne National Laboratory}
\end{minipage}

\begin{minipage}{0.5\textwidth}
	\includegraphics[width=\textwidth]{clintonpp.jpg}
	\captionof{figure}{Clinton Powerplant on Clinton Lake}
\end{minipage}
\begin{minipage}{0.5\textwidth}
	\textbf{Clinton Nuclear Power Plant}\\
Located about 35 miles away from Champaign, the Clinton Power Station is an Exelon owned nuclear power plant that started operating at full power on September 15th, 1987. They currently serve over one million customers and operate 94.9$\%$ of the time. The tour will be held on Thursday morning and bus transportation will be provided. Attendees will be guided by a Clinton employee. The tour will include the control-room simulator that operator trainees use, and a chance to learn more about the site’s innovative safety, operation, and engineering practices.
\end{minipage}

\begin{minipage}{0.5\textwidth}
	\textbf{National Pentascale Computing Facility (NPCF)}\\
Also located on campus is NCSA, which houses Blue Waters, one of the most powerful supercomputers in the world. The NCSA is within walking distance from all conference hotels. During the tour, attendees will tour the machine room and witness some of the beautiful results it produces. Supercomputers like Blue Waters are important for solving computationally challenging problems and creating robust simulations for a variety of phenomena.
\end{minipage}
\begin{minipage}{0.5\textwidth}
	\includegraphics[width=\textwidth]{bw_front.png}
	\captionof{figure}{Blue Waters Supercomputer}
\end{minipage}

@@

@@

\begin{minipage}{0.5\textwidth}
	% \centering
	\textbf{Riggs Brewery Tour}\\
For 21+ attendees, two tours of a local brewery will be included in our tours list Thursday afternoon from 3-5pm. Find out how Riggs makes their beer and taste test it along the way. Each tour will last approximately one hour and accommodates up to 20 people per tour. Riggs is located in east Urbana. Transportation to and from the brewery will be provided. 
\end{minipage}
\begin{minipage}{0.55\textwidth}
	\centering
	\includegraphics[width=0.75\textwidth]{riggs.jpg}
	\captionof{figure}{Riggs Brewery}
\end{minipage}

\begin{minipage}{0.5\textwidth}
	\centering
	\includegraphics[width=0.75\textwidth]{triptych.jpeg}
	\captionof{figure}{Triptych Brewery Vessels -- Not RPVs}
\end{minipage}
\begin{minipage}{0.5\textwidth}
% \centering
	\textbf{Triptych Brewery Tour}\\
For 21+ attendees, Triptych offers two tours that run around 1.5 hours for roughly 30 people each that includes several beer tastings throughout. Tours will be from 2-5pm on Thursday afternoon. Triptych is located in Savoy, IL, just 15 minutes from campus. Transportation to and from the brewery will be provided.
\end{minipage}

\begin{minipage}{0.5\textwidth}
	\textbf{University Tour}\\
Attendees will be able to take a tour of the UIUC campus. They will start at the Talbot Laboratory where the department of Nuclear Plasma and Radiological Engineering is located. Here, students will get to see the Virtual Education and Research Laboratory to see how virtual reality technology can be adapted and applied to educational methods. There are also many other historical artifacts on display for participants to see. Afterwards, students will be led to various noteworthy locations unique to UIUC.
\end{minipage}
\begin{minipage}{0.5\textwidth}
	\centering
	\includegraphics[width=0.75\textwidth]{creek.png}
	\captionof{figure}{Engineering Hall on the Beautiful Engineering Quad}
\end{minipage}
\\

>>>>

\subsubsection{Critical Conversations: Microreactors}
Microreactors are a growing area of nuclear research and the first installations have been projected for some time in the mid 2020s. They are capable of generating 1-50 MWth, which can be used directly or converted to electricity. These relatively portable reactors are capable of powering remote areas and towns with little infrastructure. UIUC has stated that it aims to be carbon neutral by 2050. The University is exploring the possibility of constructing a microreactor on campus for research and power generation, a first of its kind, in pursuit of its decarbonization goals. This panel will discuss the benefits and applications for microreactors around the world and also talk specifically about the potential market for microreactors on universities. We have a several groups on campus researching, simulating, and modelling microreactors. Faculty leading these groups such as Dr. Caleb Brooks and Dr. Kathryn Huff would be excellent speakers on this panel.

\subsubsection{Plasma Processing in Your Pocket}
Plasma processing has become a staple in many fields of advanced manufacturing. Without plasma, modern conveniences such as smartphones and powerful computer technology would not be possible. In this panel, representatives from companies at the cutting-edge of plasma processing research will discuss how plasmas continue to revolutionize contemporary industry. Potential panelists include Brian Jurczyk, CEO of Starfire Industries, and David Ruzic, Professor of NPRE and Principle Investigator of CPMI.

\subsubsection{Fusion: Materials for the Future}
Nuclear fusion has the potential to serve as the ultimate clean energy source, capable of supplying the world’s energy needs for millennia. Harnessing this immensely powerful energy resource requires further innovation in a variety of scientific disciplines. One of the largest remaining obstacles to fusion energy is the unprecedented strain placed on the materials from which fusion reactors are built. This panel will focus on the latest advancements in plasma facing components research and could feature panelists such as Professor Dan Andruczyk, director of the UIUC Center for Plasma-Material Interactions, and Dr. Lauren Garrison, Weinberg Fellow at ORNL.

\subsubsection{Nuclear Policy and Legislation}
Nuclear energy is one of the most heavily regulated fields in the United States. This panel aims to enlighten attendees about how legislation is written and how non-scientist government officials might better understand the potential of nuclear energy. This panel will allow attendees to learn who is working in this area and develop a network of people devoted to issues of nuclear policy. Leadership of the GAIN program would make excellent panelists to discuss policy.

\subsubsection{Radiological Techonology for a Healthier and Safer Future}
From the production of medical isotopes to nuclear verification, radiological engineering will play an important role in the future of health, security, and more. This panel will illuminate some of those applications and show attendees what could be possible with radiological technology. Speakers may include and Ross Radel from Phoenix and Professor DiFulvio from UIUC.\\

@@

\subsubsection{Science is People: Conducting Inclusive Research}
Research and technology that will help us solve the grand challenge problems of the world must also reflect the diverse needs of the people that live in it. Everyone comes to nuclear engineering from a variety of backgrounds, identities, abilities, and experiences. Saving the World One Atom at a Time means making atomic contributions. Finding ways to encourage and include even one more person in the endeavor of nuclear science is an important kind of atomic contribution. This panel works toward the goal of celebrating the people behind the science. It also serves to inspire students and professionals to consider how diversity plays a role in their research.

\subsubsection{Effective and Unorthodox Science Communication}
It has been shown that when members of the general public are given more scientific evidence they are less likely to shift their beliefs. While this finding is surprising to members of the scientific community, people who value data and evidence, it can be difficult to find ways to effectively communicate your research to the public. Professor Paul Kwiat of the Physics Department at UIUC has taken science communication in an entirely new direction. He owns and operates Lab Escape, a popular escape room in Urbana. Kwiat along with members of the Story Collider, non-profit organization devoted to helping scientists tell stories that will resonate with their audiences, would make an excellent panel on unusual methods of science communication.

\subsubsection{How to Host a Conference}
This panel is devoted to sharing the experience of this conference's planning committee with students from other schools that may want to host their own student conference. This panel is for students by students. Students from other schools will be able to ask questions and gain insights for their own conference hosting process.

@@

\subsubsection{PyNE and PyRK Workshop}
Python for Nuclear Engineering (PyNE) and Python for Reactor Kinetics (PyRK) are two open source packages with computational tools for nuclear science and engineering. The PyNE toolkit provides both a Python and a C++ API for common computational pre- and post-processing tasks in nuclear engineering. PyRK offers point kinetics implementation for nuclear reactors. This workshop will provide a hands-on tutorial for attendees to begin using PyNE and make use of its capabilities for their curriculum and research work. The Advanced Reactors and Fuel Cycles (ARFC) research group at UIUC and its collaborators will provide instructors. This workshop, alpha-tested at the University of Wisconsin will be aimed at students who can provide their own laptops and have a desire to improve their nuclear computational skills. The workshop will be approximately two hours of instruction at NCSA room 1030.

@@

Technical sessions are an integral part of every student conference. This is where students can share their research experiences, new ideas, exchange knowledge, and \textit{atomic contributions} to the big problems of the world. There are 6 technical sessions held concurrently each day. Each room will be equipped with a projectors, computers, podiums, and other necessary equipment. Each presenter is given 15 minutes to present and 5 minutes to answer questions from the audience. Presenters will be judged on significance, originality, and overall presentation (Podium Presentation Judging Form can be found in Appendix B). The divisions of the technical sessions include, but are not limited to
\begin{itemize}
	\item Accelerator Applications
	\item Aerospace Nuclear Science \& Technology
	\item Computational Medical Physics
	\item Decommissioning \& Environmental Sciences
	\item Education, Training \& Workforce Development
	\item Fuel Cycle \& Waste Management
	\item Fusion Energy
	\item Human Factors, Instrumentation \& Control
	\item Isotopes \& Radiation
	\item Materials Science \& Technology
	\item Mathematics \& Computation for Nuclear Engineering
	\item Next Generation Reactors \& Advanced Reactors
	\item Nuclear Criticality Safety
	\item Nuclear Energy Applied to Biology \& Medicine
	\item Nuclear Installations Safety
	\item Nuclear Nonproliferation
	\item Probabilistic Risk Analysis
	\item Operations \& Power
	\item Radiation Protection \& Shielding
	\item Reactor Physics
	\item Robotics \& Remote Systems
	\item Thermal Hydraulics
\end{itemize}
Practice rooms will be made available every day of the conference. We expect a total of 48 technical sessions each with 4-5 presenters. Where possible, students will be awarded with funds donated by the technical divisions of ANS.

\subsection{Poster Session}
There will be a poster session on Saturday in Illini Room C and the South Lounge. This offers nearly 1600 square feet of space and allows students an opportunity to share their research in an open environment. The poster session will be immediately adjacent to the career fair. This encourages students and professionals, that might otherwise go to one or neither, to attend both. There will be an award for best graduate and undergraduate poster. A layout of the rooms are available in Appendix D: Building Layout.

\subsubsection{Highschool Poster Session}
We believe that attracting younger students to the field of nuclear engineering will help us grow the nuclear community. To that end we will invite high school students to present a poster on a topic of interest in the nuclear sciences. This will also add to the diversity of the conference.

\subsection{Career Fair}
The career will be held all day on Friday, from 8am to 5pm, and on Saturday from 8am to noon. It will be held in Illini Rooms A \& B, a large space capable of holding 600 people. This space will be immediately adjacent to the poster sessions on saturday to encourage students and professionals to attend both. Together, the Illini Rooms can hold up to 900 people. Recruiters can mail bulkier items prior to their arrival in Champaign. All companies that sponsor the conference will be given a table at the career fair. Location will be decided in order of sponsorship amount and when the agreement was made. Universities may freely request a table at the career fair, while space is available. There will be rooms available at the Illini Union for companies to interview potential candidates.

@@

\noindent{
\begin{minipage}{0.5\textwidth}
	\textbf{National Pentascale Computing Facility (NPCF)}\\
Also located on campus is NCSA, which houses Blue Waters, one of the most powerful supercomputers in the world. The NCSA is within walking distance from all conference hotels. During the tour, attendees will tour the machine room and witness some of the beautiful results it produces. Supercomputers like Blue Waters are important for solving computationally challenging problems and creating robust simulations for a variety of phenomena.
\end{minipage}
\begin{minipage}{0.5\textwidth}
	\includegraphics[width=\textwidth]{bw_front.png}
	\captionof{figure}{Blue Waters Supercomputer}
\end{minipage}
}

@@

\noindent{
\begin{minipage}{0.5\textwidth}
\textbf{Argonne National Laboratory}\\
Located in Lemont, Illinois, Argonne works closely with universities, industry, and other national labs to help make an impact on the atomic, human, and global scale. With 14 research divisions, five national scientific user facilities, and hundreds of research partners, attendees of this tour will be exposed to the diverse areas of research in nuclear science. Argonne is two-and-a-half-hour drive away. Bus transportation will be provided. On the tour, students will be guided around the site’s scientific and engineering facilities.
\end{minipage}
\begin{minipage}{0.5\textwidth}
	\includegraphics[width=\textwidth]{argonne.png}
	\captionof{figure}{Argonne National Laboratory}
\end{minipage}}

\noindent{
\begin{minipage}{0.5\textwidth}
	\includegraphics[width=\textwidth]{clintonpp.jpg}
	\captionof{figure}{Clinton Powerplant on Clinton Lake}
\end{minipage}
\begin{minipage}{0.5\textwidth}
	\textbf{Clinton Nuclear Power Plant}\\
Located about 35 miles away from Champaign, the Clinton Power Station is an Exelon owned nuclear power plant that started operating at full power on September 15th, 1987. They currently serve over one million customers and operate 94.9$\%$ of the time. The tour will be held on Thursday morning and bus transportation will be provided. Attendees will be guided by a Clinton employee. The tour will include the control-room simulator that operator trainees use, and a chance to learn more about the site’s innovative safety, operation, and engineering practices.
\end{minipage}}

@@

\noindent{\begin{minipage}{0.5\textwidth}
	% \centering
	\textbf{Riggs Brewery Tour}\\
For 21+ attendees, two tours of a local brewery will be included in our tours list Thursday afternoon from 3-5pm. Find out how Riggs makes their beer and taste test it along the way. Each tour will last approximately one hour and accommodates up to 20 people per tour. Riggs is located in east Urbana. Transportation to and from the brewery will be provided. 
\end{minipage}
\begin{minipage}{0.55\textwidth}
	\centering
	\includegraphics[width=0.75\textwidth]{riggs.jpg}
	\captionof{figure}{Riggs Brewery}
\end{minipage}}

\noindent{
\begin{minipage}{0.5\textwidth}
	\centering
	\includegraphics[width=0.75\textwidth]{triptych.jpeg}
	\captionof{figure}{Triptych Brewery Vessels -- Not RPVs}
\end{minipage}
\begin{minipage}{0.5\textwidth}
% \centering
	\textbf{Triptych Brewery Tour}\\
For 21+ attendees, Triptych offers two tours that run around 1.5 hours for roughly 30 people each that includes several beer tastings throughout. Tours will be from 2-5pm on Thursday afternoon. Triptych is located in Savoy, IL, just 15 minutes from campus. Transportation to and from the brewery will be provided.
\end{minipage}}

\noindent{\begin{minipage}{0.5\textwidth}
	\textbf{University Tour}\\
Attendees will be able to take a tour of the UIUC campus. They will start at the Talbot Laboratory where the department of Nuclear Plasma and Radiological Engineering is located. Here, students will get to see the Virtual Education and Research Laboratory to see how virtual reality technology can be adapted and applied to educational methods. There are also many other historical artifacts on display for participants to see. Afterwards, students will be led to various noteworthy locations unique to UIUC.
\end{minipage}
\begin{minipage}{0.5\textwidth}
	\centering
	\includegraphics[width=0.75\textwidth]{creek.png}
	\captionof{figure}{Engineering Hall on the Beautiful Engineering Quad}
\end{minipage}}
\\
